---
title: "data-cleaning"
author: "Logan Williams"
date: "12/3/2021"
output: html_document
params:
  wk: 7
  year: 2023
  month: "March"
  monthlyTracker: "https://docs.google.com/spreadsheets/d/1zS9KHYaF8hkdCaIK2WDkM9mMxwPI9QO1FAjl-rpK2xA/edit#gid=30792091"
  gtmTracker: "https://docs.google.com/spreadsheets/d/1hMI2wEZMa69btaD6Rw9JDy4WdEgjvM21v0S1G5NerRA/edit#gid=170885893"
---

```{r, warning = false}
#load dependencies
library(openxlsx)   #tools for saving xls data
library(readxl)     #load xlsx data
library(dplyr)      #tools for cleaning data
library(here)       #file path management
library(janitor)    #row to colheader conversion
library(lubridate)  #date/time manipulation
library(scales)     #percent format
library(zoo)        #handle infinite values
library(stringr)    #remove whitespaces
library(googlesheets4) #update google sheets

storelist <- read_excel(here("data/base_data/storelist.xlsx"))
storelist$StoreNumber <- as.character(storelist$StoreNumber)
#load Walmart Week data
weeks <- read_excel(here("data", params$year, "Walmart Weeks.xlsx"))

#filter for current week
if(params$wk < 10){
  this_week <- filter(weeks, `WM Week` == paste(params$year, 0, params$wk, sep = ""))
}else if(params$wk > 48){
  this_week <- filter(weeks, `WM Week` == paste(params$year-1, params$wk, sep = ""))
}else{
  this_week <- filter(weeks, `WM Week` == paste(params$year, params$wk, sep = ""))
}

#get current month for file paths
month <- params$month
```

```{r, warning=false}
# Create results folder path for current week
here::here()
dir.create(getwd())
dir.create(here::here(file.path("results", params$year)))
dir.create(here::here(file.path("results", params$year, month)))
dir.create(here::here(file.path("results", params$year, month, paste("Week", params$wk, sep = ""))))
```

#In Store Data
```{r}
#load data
raw_store <- read_excel(here("data", params$year, month, paste("Week", params$wk, sep = ""), "store.xlsx"), sheet = 1)
#remove empty rows
store <- raw_store[!is.na(raw_store[1]),]
#add first row as column headers
store <- janitor::row_to_names(store, 1)

#separate data between inventory and this weeks sales
if(params$wk < 10){
  inventory <- filter(store, `WM Week` == paste(params$year, 0,params$wk+1, sep = ""))
  sales <- filter(store, `WM Week` == paste(params$year, 0, params$wk, sep = ""))
}else if(params$wk >= 48){
  inventory <- filter(store, `WM Week` == paste(params$year-1, params$wk+1, sep = ""))
  sales <- filter(store, `WM Week` == paste(params$year-1, params$wk, sep = ""))
}else{
  inventory <- filter(store, `WM Week` == paste(params$year, params$wk+1, sep = ""))
  sales <- filter(store, `WM Week` == paste(params$year, params$wk, sep = ""))
}

#transform sales data to numeric to prep for summarise
sales$`POS Qty` <- as.numeric(sales$`POS Qty`)
sales$`POS Sales` <- as.numeric(sales$`POS Sales`)
sales$`Total Customer Item Return` <- as.numeric(sales$`Total Customer Item Return`)

#create pivot table
sales%>%
  group_by(`WM Week`, `Brand Desc`, `Vendor Stk Nbr`, `Item Nbr`, `Item Flags`, `UPC`)%>%
  summarise(`POS Qty` = sum(`POS Qty`), `POS Sales` = sum(`POS Sales`), `Total Customer Item Return` = sum(`Total Customer Item Return`)) -> sales_pvt

#enter blank values for Item Flags
sales_pvt$`Item Flags` <- ""

#add week end/start, store nbr, and Curr columns
sales_pvt%>%
  mutate(WeekStart = this_week$WeekStart, .before = `WM Week`)%>%
  mutate(WeekEnd = this_week$WeekEnd, .before = `WM Week`)%>%
  mutate(`Store Nbr` = 0, .after = `WM Week`)%>%
  mutate(`Curr Str On Hand Qty` = 0)%>%
  mutate(`Curr Instock %` = 0)%>%
  mutate(`Curr Str On Order Qty` = 0)%>%
  mutate(`Curr Str In Transit Qty` = 0)-> sales_pvt

#remove time from date field
sales_pvt$WeekStart <- as.Date(sales_pvt$WeekStart)
sales_pvt$WeekEnd <- as.Date(sales_pvt$WeekEnd)
```

#Sales by SKU by Store
```{r}
#create pivot table
sales%>%
  mutate(GrossUnit = `POS Qty`+`Total Customer Item Return`)%>%
  group_by(`WM Week`, `Store Nbr`, `Item Nbr`, `UPC`)%>%
  summarise(Net_Unit = sum(`POS Qty`), Net_Sales = sum(`POS Sales`), Gross_Unit = sum(GrossUnit), Return_Unit = sum(`Total Customer Item Return`), GrossPOS = sum(Gross_Unit*(Net_Sales/Net_Unit)))->skuByStore

#replace missing/infinite values with 0
skuByStore$GrossPOS[is.na(skuByStore$GrossPOS)] <- 0
skuByStore$GrossPOS[is.infinite(skuByStore$GrossPOS)] <- 0
         
#add week end/start, store nbr, and Curr columns
skuByStore%>%
  mutate(WeekStart = this_week$WeekStart, .before = `WM Week`)%>%
  mutate(WeekEnd = this_week$WeekEnd, .after = `WM Week`)%>%
  mutate(`Curr Str On Hand Qty` = 0, .before = GrossPOS)%>%
  mutate(`Curr Instock %` = 0, .after = `Curr Str On Hand Qty`)%>%
  mutate(`Curr Str On Order Qty` = 0, .after = `Curr Instock %`)%>%
  mutate(`Curr Str In Transit Qty` = 0, .after = `Curr Str On Order Qty`)%>%
  dplyr::select(WeekStart, `WM Week`, WeekEnd, `Store Nbr`, `Item Nbr`, UPC, Net_Unit, Net_Sales, Gross_Unit, Return_Unit, `Curr Str On Hand Qty`,
                `Curr Instock %`, `Curr Str On Order Qty`, `Curr Str In Transit Qty`, GrossPOS)-> skuByStore

#remove time from date field
skuByStore$WeekStart <- as.Date(skuByStore$WeekStart)
skuByStore$WeekEnd <- as.Date(skuByStore$WeekEnd)
```

#SQL Data Upload Prep
```{r}
#create pivot table
sales%>%
  group_by(`WM Week`, `Store Nbr`, `Item Nbr`, `UPC`, `Brand Desc`)%>%
  summarise(Net_Unit = sum(`POS Qty`), Net_Sales = sum(`POS Sales`), Return_Unit = sum(`Total Customer Item Return`))->sql
         
#add week end/start, store nbr, and Curr columns
sql%>%
  mutate(WeekStart = this_week$WeekStart, .before = `WM Week`)%>%
  mutate(WeekEnd = this_week$WeekEnd, .after = `WM Week`)%>%
  mutate(`Curr Str On Hand Qty` = 0)%>%
  mutate(`Curr Instock %` = 0, .after = `Curr Str On Hand Qty`)%>%
  mutate(`Curr Str On Order Qty` = 0, .after = `Curr Instock %`)%>%
  mutate(`Curr Str In Transit Qty` = 0, .after = `Curr Str On Order Qty`)%>%
  dplyr::select(WeekStart, `Brand Desc`, `WM Week`, WeekEnd, `Store Nbr`, `Item Nbr`, UPC, Net_Unit, Net_Sales, Return_Unit, `Curr Str On Hand Qty`,
                `Curr Instock %`, `Curr Str On Order Qty`, `Curr Str In Transit Qty`)-> sqlClean

#remove time from date field
sqlClean$WeekStart <- as.Date(sqlClean$WeekStart)
sqlClean$WeekEnd <- as.Date(sqlClean$WeekEnd)
```

#Aggregate Sales by Store
```{r}
sales%>%
  mutate(WeekEnd = this_week$WeekEnd, .after = `WM Week`) -> salesByStore

skuByStore%>%
  group_by(`WM Week`, WeekEnd, `Store Nbr`)%>%
  summarise(POS_Unit = sum(Net_Unit), POS_Sales = sum(Net_Sales), Gross_Unit = sum(Gross_Unit), Gross_POS = sum(GrossPOS), Return_Unit = sum(Return_Unit))->salesByStore
```

#Check Totals
```{r}
salesCheck <- sum(sales$`POS Qty`)+sum(sales$`Total Customer Item Return`)
if(sum(salesByStore$Gross_Unit) != salesCheck) stop("Error in salesByStore gross unit total")
if(sum(sales_pvt$`POS Qty`)+sum(sales_pvt$`Total Customer Item Return`) != salesCheck) stop("Error in sales_pvt gross unit total")
if(sum(skuByStore$Gross_Unit) != salesCheck) stop("Error in skuByStore gross unit total")
```

#Online Data
```{r}
#load online data
online <- read_excel(here("data", params$year, month, paste("Week", params$wk, sep = ""), "online.xlsx"))
#add POS Sales column
online <- mutate(online, `POS Sales` = `Average Unit Retail`*`Net Units`)

#Rename columns, mutate columns to perform calculations
online%>%
  mutate(WeekStart = this_week$WeekStart)%>%
  mutate(WeekEnd = this_week$WeekEnd)%>%
  mutate(`Store Nbr` = 99999)%>%
  mutate(`WM Week` = this_week$`WM Week`)%>%
  mutate(`POS Sales` = `Average Unit Retail`*`Net Units`)%>%
  mutate(`Curr Str On Hand Qty` = 0)%>%
  mutate(`Curr Instock %` = 0)%>%
  mutate(`Curr Str On Order Qty` = 0)%>%
  mutate(`Curr Str In Transit Qty` = 0)%>%
  mutate(`Item Flags` = "")%>%
  select(WeekStart, WeekEnd, `WM Week`, `Store Nbr`, `BRAND_NAME`, `CATLG_ITEM_ID`, `WM_ITEM_NUMBER (Dotcom)`, `Item Flags`, WUPC, `Net Units`, `POS Sales`, `Return Units`, `Curr Str On Hand Qty`, `Curr Instock %`, `Curr Str On Order Qty`, `Curr Str In Transit Qty`)-> onlineTransformed

onlineTransformed%>%
  rename(`Brand Desc` = `BRAND_NAME`)%>%
  rename(`Vendor Stk Nbr` = `CATLG_ITEM_ID`)%>%
  rename(`Item Nbr` = `WM_ITEM_NUMBER (Dotcom)`)%>%
  rename(UPC = WUPC)%>%
  rename(`POS Qty` = `Net Units`)%>%
  rename(`Total Customer Item Return` = `Return Units`)-> online_clean


#remove time from date field
online_clean$WeekStart <- as.Date(online_clean$WeekStart)
online_clean$WeekEnd <- as.Date(online_clean$WeekEnd)

#Create Online Data for skuByStore Merge
online_clean%>%
  mutate(Gross_Unit = `POS Qty`+`Total Customer Item Return`)%>%
  mutate(GrossPOS = Gross_Unit*(`POS Sales`/`POS Qty`))%>%
  rename(Return_Unit = `Total Customer Item Return`)%>%
  rename(Net_Sales = `POS Sales`)%>%
  rename(Net_Unit = `POS Qty`)%>%
  dplyr::select(WeekStart, `WM Week`, WeekEnd, `Store Nbr`, `Item Nbr`, UPC, Net_Unit, Net_Sales, Gross_Unit, Return_Unit, `Curr Str On Hand Qty`,
                `Curr Instock %`, `Curr Str On Order Qty`, `Curr Str In Transit Qty`, GrossPOS) -> skuByOnline

#replace missing/infinite values with 0
skuByOnline$GrossPOS[is.na(skuByOnline$GrossPOS)] <- 0
skuByOnline$GrossPOS[is.infinite(skuByOnline$GrossPOS)] <- 0
```

#Merge Online and In Store Data
```{r}
##############
#Sales by SKU#
##############
#create column index
cols.num <- c(3,4,9:13, 15,16)
#prep for merge, make sure columns have same class
sales_pvt[cols.num] <- sapply(sales_pvt[cols.num],as.numeric)
sales_pvt[7] <- sapply(sales_pvt[7],as.character)
online_clean[cols.num] <- sapply(online_clean[cols.num],as.numeric)
online_clean$`Vendor Stk Nbr`<- as.character(online_clean$`Vendor Stk Nbr`)
#merge
tot_sales <- bind_rows(sales_pvt, online_clean)

##############
#SKU by store#
##############
#prep data for merge
skuByOnline[c(2,4,6)] <- sapply(skuByOnline[c(2,4,6)],as.character)

#Merge Store by Sku and Online by Sku
skuByStoreClean <- bind_rows(skuByStore,skuByOnline)

################
#Sales by store#
################
skuByOnline%>%
  rename(POS_Unit = Net_Unit)%>%
  rename(POS_Sales = Net_Sales)%>%
  rename(Gross_POS = GrossPOS)%>%
  dplyr::select(`WM Week`, `WeekEnd`, `Store Nbr`, POS_Unit, POS_Sales, Gross_Unit, Gross_POS, Return_Unit) -> tempOnline

salesByStore <- bind_rows(salesByStore, tempOnline)

#################
#SQL Upload Data#
#################
online_clean%>%
  rename(Net_Unit = `POS Qty`)%>%
  rename(Net_Sales = `POS Sales`)%>%
  rename(Return_Unit = `Total Customer Item Return`)%>%
  dplyr::select(`WeekStart`, `Brand Desc`, `WM Week`, WeekEnd, `Store Nbr`, `Item Nbr`, UPC, Net_Unit, Net_Sales, Return_Unit, `Curr Str On Hand Qty`, `Curr Instock %`, `Curr Str On Order Qty`, `Curr Str In Transit Qty`) -> onlineSql

onlineSql[c(3,5,7)] <- sapply(onlineSql[c(3,5,7)],as.character)

sqlClean <- bind_rows(sqlClean, onlineSql)
```

#Prep Inventory Variables for SQL Upload
```{r}
#create column index
cols.num.inv <- c(1,5,7:14)
#prep for merge, make sure columns have same class
inventory[cols.num.inv] <- sapply(inventory[cols.num.inv],as.numeric)
inventory%>%
  group_by(`WM Week`, `Brand Desc`, `Vendor Stk Nbr`, `Item Nbr`, `Item Flags`, `UPC`)%>%
  summarise()
```

# Check for New UPCs
```{r}
upcList <- read_sheet(params$gtmTracker, sheet = "WMT: SKU | Sales [2023]", range = "B3:B170")

#check for missing UPCs
missingUpc <- c()
checkUpc <- unique(tot_sales$UPC)
for(line in checkUpc){
    line <- str_trim(line)
    if(line %in% upcList$Retailer_ID){
      #do nothing
    }else{
      #create list of UPCs that need to be added to GTM Tracker
      missingUpc <- c(missingUpc, line)
    }
}

#crete empty object to store UPCs for Stop statement
upcOutput <- ""
i <- 1
  if(length(missingUpc) > 0){
    {stop(length(missingUpc), " new UPCs: ", 
          while(i <= length(missingUpc)){
            upcOutput <- paste(upcOutput, missingUpc[i], sep = "\n")
            i <- i+1
            }, upcOutput)}
  }
```

#Check Totals
```{r}
totSalesCheck <- salesCheck + sum(online$`Net Units`) + sum(online$`Return Units`)
tot_salesGross <- sum(tot_sales$`POS Qty`)+sum(tot_sales$`Total Customer Item Return`)
if(tot_salesGross != totSalesCheck) stop("error: tot_sales gross units ", tot_salesGross, " but should be ", totSalesCheck)

if(sum(salesByStore$Gross_Unit) != totSalesCheck) stop("Error: salesByStore gross units:", sum(salesByStore$Gross_Unit), " but should be ", totSalesCheck)

if(sum(skuByStoreClean$Gross_Unit) != totSalesCheck) stop("Error: skuByStoreClean gross units: ", sum(skuByStoreClean$Gross_Unit), " but should be ", totSalesCheck)

sqlGross <- sum(sqlClean$Net_Unit)+sum(sqlClean$Return_Unit)
if(sqlGross != totSalesCheck) stop("Error: sqlClean gross unit total: ", sqlGross, " but should be ", totSalesCheck)
```

#Save Merged Output
```{r}
# Create a blank workbook
store_wb <- createWorkbook()

# Add some sheets to the workbook
addWorksheet(store_wb, "Sales")
addWorksheet(store_wb, "Raw Data")
addWorksheet(store_wb, "Inventory")
addWorksheet(store_wb, "Store Data")
addWorksheet(store_wb, "SKU by Store")
addWorksheet(store_wb, "SQL Upload")


# Write the data to the sheets
writeData(store_wb, sheet = "Sales", x = tot_sales)
writeData(store_wb, sheet = "Raw Data", x = raw_store)
writeData(store_wb, sheet = "Inventory", x = inventory)
writeData(store_wb, sheet = "Store Data", x = salesByStore)
writeData(store_wb, sheet = "SKU Inv Monthly", x = inv_tot)
writeData(store_wb, sheet = "SQL Upload", x = sqlClean)

# Export the file
saveWorkbook(store_wb, here("results", params$year, month, paste("Week", params$wk, sep = ""), paste("Google Weekly Recap (Stores) - Week ", params$wk, ".xlsx", sep = "")), overwrite = TRUE)
```

#Save Online Output
```{r}
# Create a blank workbook
online_wb <- createWorkbook()

# Add some sheets to the workbook
addWorksheet(online_wb, "Chromebooks")
addWorksheet(online_wb, "Sales")


# Write the data to the sheets
writeData(online_wb, sheet = "Chromebooks", x = online)
writeData(online_wb, sheet = "Sales", x = online_clean)

# Export the file
saveWorkbook(online_wb, here("results", params$year, month, paste("Week", params$wk, sep = ""), paste("Google Weekly Recap (dotcom) - Week ", params$wk, ".xlsx", sep = "")), overwrite = TRUE)
```

```{r}
#Everything below is code in progress
stop("Code finished executing. Workbooks successfully saved")
```




#Google Sheet Uploading
###Weekly Sales (Monthly Tracker)

```{r}
#Merge Online w/SKU Level Sales by store
onlineTransformed%>%
  rename(`Item Nbr` = `WM_ITEM_NUMBER (Dotcom)`)%>%
  rename(UPC = WUPC)%>%
  rename(Net_Unit = `Net Units`)%>%
  rename(Net_Sales = `POS Sales`)%>%
  rename(Return_Unit = `Return Units`)-> onlineSalesBySku

onlineSalesBySku%>%
  mutate(Gross_Unit = Net_Unit+Return_Unit)%>%
  mutate(NetASP = Net_Sales/Net_Unit)%>%
  mutate(GrossPOS = Gross_Unit*NetASP) -> onlineSalesBySku

onlineSalesBySku$GrossPOS[is.na(onlineSalesBySku$GrossPOS)] <- 0
onlineSalesBySku$GrossPOS[is.infinite(onlineSalesBySku$GrossPOS)] <- 0

onlineSalesBySku <- dplyr::select(onlineSalesBySku, `WM Week`, WeekEnd, `Store Nbr`, `Item Nbr`, UPC, Net_Unit, Net_Sales, Gross_Unit, Return_Unit,`Curr Str On Hand Qty`, `Curr Instock %`, `Curr Str On Order Qty`, `Curr Str In Transit Qty`, GrossPOS)

onlineSalesBySku$`WM Week` <- as.character(onlineSalesBySku$`WM Week`)
onlineSalesBySku$`Store Nbr` <- as.character(onlineSalesBySku$`Store Nbr`)

skuByStoreBind <- dplyr::select(skuByStore, -WeekStart)
weeklySales <- bind_rows(skuByStoreBind, onlineSalesBySku)
skuLevelStorelist <- dplyr::select(storelist, StoreNumber, PilotStoreType, Region, Market, Pair)
weeklySales <- left_join(weeklySales, skuLevelStorelist, by = c("Store Nbr" = "StoreNumber"))

tot_sales%>%
  dplyr::select(`WM Week`, `Brand Desc`, `Vendor Stk Nbr`, `Item Nbr`, `Item Flags`, UPC, `POS Qty`, `POS Sales`, `Total Customer Item Return`, `WeekEnd`) -> salesBySkuUpload

#Upload To Monthly Tracker
lastWeekData <- read_sheet(params$monthlyTracker, "Weekly Sales")
if(is.na(unique(lastWeekData$`WM Week`))){
  print("Sheet is empty")}else if (unique(lastWeekData$`WM Week`) != this_week$`WM Week`){
    write_sheet(lastWeekData, params$monthlyTracker, "Previous Week Sales")
}
write_sheet(weeklySales, params$monthlyTracker, "Weekly Sales")
sheet_append(params$monthlyTracker, weeklySales, sheet = "Current Month Sales")
```

# SalesBySKU Tab
```{r}

#Upload SKU level data
skuLevelSales <- read_sheet(params$monthlyTracker, "SalesBySKU")
if(unique(salesBySkuUpload$`WM Week`) %in% skuLevelSales$`WM Week`){
  skuLevelSales <- filter(skuLevelSales, `WM Week` != unique(salesBySkuUpload$`WM Week`))
  skuLevelSales <- bind_rows(skuLevelSales, salesBySkuUpload)
}else{
  
}
if(is.na(unique(lastWeekData$`WM Week`))){
  print("Sheet is empty")}else if (unique(lastWeekData$`WM Week`) != this_week$`WM Week`){
    write_sheet(lastWeekData, params$monthlyTracker, "Previous Week Sales")
}
write_sheet(weeklySales, params$monthlyTracker, "Weekly Sales")
sheet_append(params$monthlyTracker, weeklySales, sheet = "Current Month Sales")
```


###Pilot Level Sales Tracker
```{r}
#create df to merge with Sales by Store
online_clean%>%
  mutate(GrossUnit = `POS Qty`+`Total Customer Item Return`)%>%
  mutate(NetASP = `POS Sales`/`POS Qty`)%>%
  mutate(GrossPOS = GrossUnit*NetASP)-> onlineSum

onlineSum$GrossPOS[is.na(onlineSum$GrossPOS)] <- 0
onlineSum$GrossPOS[is.infinite(onlineSum$GrossPOS)] <- 0
    
onlineSum%>%
  group_by(`WM Week`, WeekEnd, `Store Nbr`)%>%
  summarise(POS_Unit = sum(`POS Qty`), POS_Sales = sum(`POS Sales`), Gross_Unit = sum(`POS Qty`,`Total Customer Item Return`), Gross_POS = sum(GrossPOS), Return_Unit = sum(`Total Customer Item Return`)) -> onlineSum

onlineSum$`WM Week` <- as.character(onlineSum$`WM Week`)
onlineSum$`Store Nbr` <- as.character(onlineSum$`Store Nbr`)
storeSalesClean <- bind_rows(salesByStore, onlineSum)

storelistTrim <- dplyr::select(storelist, StoreNumber, StoreType...12, PilotStoreType, Market, Region, Pair)
storeSalesClean <- left_join(storeSalesClean, storelistTrim, by = c("Store Nbr" = "StoreNumber"))

#Upload to pilot level sales tracker
liveStoreLevelData <- read_sheet("https://docs.google.com/spreadsheets/d/1K4pMJXAjONXEmAJbN55BHzyU2BQuVWm6hy4Rr0p1ANA/edit#gid=415770348", "Data")
nonCurrentWeek <- filter(liveStoreLevelData, `WM Week` != this_week$`WM Week`)
nonCurrentWeek$`WM Week` <- as.character(nonCurrentWeek$`WM Week`)
nonCurrentWeek$`Store Nbr` <- as.character(nonCurrentWeek$`Store Nbr`)
updatedAllWeeks <- bind_rows(nonCurrentWeek, storeSalesClean)
write_sheet(updatedAllWeeks, "https://docs.google.com/spreadsheets/d/1K4pMJXAjONXEmAJbN55BHzyU2BQuVWm6hy4Rr0p1ANA/edit#gid=415770348", "Data")
```



#Manual Input Online Only Calculations
```{r}
online$`POS Sales`[is.na(online$`POS Sales`)] <- 0
online%>%
  summarise(`Sum Net Units` = sum(`Net Units`), `Sum Return Units` = sum(`Return Units`), `Net Sales` = sum(`POS Sales`))%>%
  knitr::kable()
```

#Slide 5 Total ASP
```{r}
#calculate necessary values
tot_sales%>%
  mutate(`Gross Unit` = sum(`POS Qty`+`Total Customer Item Return`))%>%
  mutate(`NetASP` = `POS Sales`/`POS Qty`)%>%
  mutate(`GrossPOS Sales` = `Gross Unit`*`NetASP`)-> asp

#replace missing values with zero
asp$`Gross Unit`[is.na(asp$`Gross Unit`)] <- 0
asp$NetASP[is.na(asp$NetASP)] <- 0
asp$`GrossPOS Sales`[is.na(asp$`GrossPOS Sales`)] <- 0
asp$`Gross Unit`[is.infinite(asp$`Gross Unit`)] <- 0
asp$NetASP[is.infinite(asp$NetASP)] <- 0
asp$`GrossPOS Sales`[is.infinite(asp$`GrossPOS Sales`)] <- 0

#return ASP
round(sum(asp$`GrossPOS Sales`)/sum(asp$`Gross Unit`))
```
#Online ASP
```{r}
#calculate necessary values
online_clean%>%
  mutate(`Gross Unit` = (`POS Qty`+`Total Customer Item Return`))%>%
  mutate(`NetASP` = `POS Sales`/`POS Qty`)%>%
  mutate(`GrossPOS Sales` = `Gross Unit`*`NetASP`)-> asp_online

#replace missing values with zero
asp_online$`Gross Unit`[is.na(asp_online$`Gross Unit`)] <- 0
asp_online$NetASP[is.na(asp_online$NetASP)] <- 0
asp_online$`GrossPOS Sales`[is.na(asp_online$`GrossPOS Sales`)] <- 0

#return ASP
round(sum(asp_online$`GrossPOS Sales`)/sum(asp_online$`Gross Unit`))
```

#In Store ASP
```{r}
#calculate necessary values
sales_pvt%>%
  mutate(`Gross Unit` = sum(`POS Qty`+`Total Customer Item Return`))%>%
  mutate(`NetASP` = `POS Sales`/`POS Qty`)%>%
  mutate(`GrossPOS Sales` = `Gross Unit`*`NetASP`)-> inStoreAsp

#replace missing values with zero
inStoreAsp$`Gross Unit`[is.na(inStoreAsp$`Gross Unit`)] <- 0
inStoreAsp$NetASP[is.na(inStoreAsp$NetASP)] <- 0
inStoreAsp$`GrossPOS Sales`[is.na(inStoreAsp$`GrossPOS Sales`)] <- 0
inStoreAsp$`Gross Unit`[is.infinite(inStoreAsp$`Gross Unit`)] <- 0
inStoreAsp$NetASP[is.infinite(inStoreAsp$NetASP)] <- 0
inStoreAsp$`GrossPOS Sales`[is.infinite(inStoreAsp$`GrossPOS Sales`)] <- 0

#return ASP
round(sum(inStoreAsp$`GrossPOS Sales`)/sum(inStoreAsp$`Gross Unit`))
```

#Build Online Monthly Dataframe
```{r}
#Build master dataset to be added onto each month
if (file.exists(here("results", params$year, month, "month-online-clean.rda")) == TRUE){
  #load master data
  load(file = here::here("results", params$year, month, "month-online-clean.rda"))
  #add current week to monthly master data
  base_online <- bind_rows(base_online, online_clean)
  save(base_online, file = here::here("results", params$year, month, "month-online-clean.rda"))
}else{
  base_online <- online_clean
save(base_online, file = here::here("results", params$year, month, "month-online-clean.rda"))
}
```

#Build Total Sales Monthly Dataframe
```{r}
#Build master dataset to be added onto each month
if (file.exists(here("results", params$year, month, "month-store-clean.rda")) == TRUE){
  #load master data
  load(file = here::here("results", params$year, month, "month-store-clean.rda"))
  #add current week to monthly master data
  base_store <- bind_rows(base_store, tot_sales)
  save(base_store, file = here::here("results", params$year, month, "month-store-clean.rda"))
}else{
base_store <- tot_sales
save(base_store, file = here::here("results", params$year, month, "month-store-clean.rda"))
}
```

#Top Selling SKUs (Weekly)
```{r}
sku_ref <- read_excel(here("data/base_data/sku_ref.xlsx"))

sales_pvt%>%
  mutate(gross_unit = `Total Customer Item Return` + `POS Qty`)%>%
  select(`Item Nbr`, gross_unit)-> top_sku

top_sku_clean <- inner_join(top_sku, sku_ref)
```



